### 2024-03-06 README.Rmd
style pkg files

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
library('mgcv')
library('gratia')
```

@@

* Estimatation of derivatives of fitted smoothers: `derivatives()`,

@@

```{r install, eval = FALSE}
install.packages('gratia')
```

@@

```{r install-r-universe, eval = FALSE}
# Install gratia in R
install.packages("gratia", repos = c("https://gavinsimpson.r-universe.dev",
  "https://cloud.r-project.org"))
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
library("mgcv")
library("gratia")
```

@@

* Estimation of derivatives of fitted smoothers: `derivatives()`,

@@

```{r install, eval = FALSE}
install.packages("gratia")
```

@@

```{r install-r-universe, eval = FALSE}
# Install gratia in R
install.packages("gratia", repos = c(
  "https://gavinsimpson.r-universe.dev",
  "https://cloud.r-project.org"
))
```
